### 2015-07-02 narrative/naming-service.tex
start to reshape the proposal
naming/discovery service.

\subsubsection{Naming and Discovery Service}

@@

Our goal with this proposal is to offer a similar capability but with a finer
granularity leveraging the inner structure of scientific data, 
and manage discovering efficiently, where the data may
be split and placed on several storage layers, or may have migrated
based on system pressures. Instead of a single file such as might be used to
store an entire timestep output for a simulation, we will demonstrate offering
the same capability at a subset of a single variable level. By shifting to a
finer-grained approach, we will enable more effective use of close/fast/small
storage tiers and manage the impact when there is insufficient space forcing
data to move. Traiditional HSM stores an entire file on a tier making room if
insufficient space is available. With this shift to a partial variable
granularity, a 1 PB output with 500 GB of ``high interest'' data can limit this
costly tier ussage to just 500 GB greatly enhancing usability. This reduces
pressure forcing data migration, but does not prevent it. We still need to be
able to find the data should it move based on system pressure.

The resulting naming and discovery service will attach the Sirocco
contaier/object/fork/address tuple with a special attribute indicating that
this record is of ``high interest'' strongly encouraging keeping the variable
in close/fast/small storage as long as possible. In addition to maintaining
this additional metadata, the application and/or middleware must provide this
information. The storage system simply needs to act appropriately on this data
based on the attribute.

>>>>

\subsection{Naming and Discovery Service}

@@

Our goal with this proposal is to offer a similar capability but with a finer
granularity, leveraging the inner structure of scientific data,
and manage data discovery efficiently, where the data may
be split and placed on several storage layers, or may have migrated
based on system pressures or user or system policies. Instead of a single file such as might be used to
store an entire timestep output for a simulation, we will demonstrate extending
this capability to a subset of a single variable level. By shifting to a
finer-grained approach, we will enable more effective use of close/fast/small
storage tiers and prioritize objects with high importance.
Traiditional HSM stores an entire file on a tier making room if
insufficient space is available. With this shift to a partial variable
granularity, a 1 PB output with 200 GB of ``high interest'' data can limit this
costly tier ussage to just 200 GB greatly, improving usability and performance while still
allowing science to be done. This effectively reduces
pressure forcing data migration. Meanwhile, we need to be
able to locate the data should it moves.
Utilizing the description of data (section \ref{}) informed by users and packed by the middleware,
the resulting naming and discovery service will attach the Sirocco
contaier/object/fork/address tuple with a special attribute indicating that
this record is of ``high interest'' strongly encouraging keeping the record
in close/fast/small storage as long as possible.
